Effects of pulsed hollow electron lens operation on the beam core in HL-LHC: \\First experimental studies and simulations.

### 2018-02-12 resex.tex
add 2016 filling scheme

\section{LHC experiments on the effect of a resonant and random excitation on the beam core\label{sec:exp}}
%put picture on top
\begin{figure*}
	\begin{minipage}[t]{1.0\linewidth}
		\centering
		2016 experiment \textcolor{red}{(update picture)}\\
		\includegraphics[width=0.7\linewidth]{bunchfilling.png}	
	\end{minipage}
	\begin{minipage}[t]{1.0\linewidth}
		\centering
		$ $\\
		2017 experiment\\
		\includegraphics[width=0.7\linewidth]{bunchfilling.png}	
	\end{minipage}
	\caption{\label{fig:fill} Filling and excitation scheme for LHC experiments in 2016 (top) and 2017 (bottom).}
\end{figure*}
%put picture on top

>>>>

\section{LHC experiments on the effect of a resonant and random excitation on the beam core\label{sec:exp}}
%put picture on top
\begin{figure*}
	\begin{minipage}[t]{1.0\linewidth}
		\centering
		2016 experiment\\
		\includegraphics[width=0.7\linewidth]{bunchfilling_2016.png}	
	\end{minipage}
	\begin{minipage}[t]{1.0\linewidth}
		\centering
		$ $\\
		2017 experiment\\
		\includegraphics[width=0.7\linewidth]{bunchfilling_2017.png}	
	\end{minipage}
	\caption{\label{fig:fill} Filling and excitation scheme for LHC experiments in 2016 (top) and 2017 (bottom). In 2016 the same excitation amplitude was applied on a group of 4 bunch while in 2016 the number was increased to 6 bunches. In 2016 the excitation was also only applied in one plane leading to $2\times24=48$ bunches in total in 2016 and $3\times2\times36=216$ bunches in 2017.}
\end{figure*}
%put picture on top
